Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
blahdy blah

\begin{abstract}
Although people naturally rely upon multiple, diverse information sources in the course of routine problem-solving and decision-making tasks, support for data integration in Personal Information Management (PIM) tools remains poor, if largely nonexistent. This paper presents an exploratory, sequential, mixed-method study of ways to extend PIM tools to support user-driven data integration while performing their primary tasks. We present results of two pre-study in which requirements, we designed and evaluated DataPalette.  
% We find that the ``light-touch'' data integration mechanisms introduced allow people to effectively work with and combine information from multiple sources, and more thoroughly justify their choices 
%% exploratory, sequential mixed-method study of 
\end{abstract}

@@

We performed an exploratory sequential mixed-method study to help us design our contribution. For our first pre-study, we sought an updated understanding on the use of multiple information sources in information gathering on the Web. There were two driving questions behind this inquiry; first, were people increasingly relying only on a handful of ``supersites'' (Facebook, Wikipedia), or searching across distributed sources of information?  If the former were true, merely integrating PIM tools with the small number of supersites would provide greater benefit than tackling the substantially more challenging problem of integrating data from arbitrary sources on the Web.  Second, why did people choose a single or multiple sources for information gathering?  If a number of websites were used, why was this preferred over a single source?

@@

\subsubsection{Results - Heterogeneous Data Tasks}

The 8 participants, recruited informally via word of mouth, consisted of 7 male and 1 female. They were split evenly into two age groups of 18-25 and 26-32.   
% mention # that were computer scientists here?

>>>>

\begin{abstract}
While people naturally draw from diverse information sources in the course of routine decision-making, complementary support for managing diverse, heterogeneous data in digital Personal Information Management (PIM) tools remains poor.  In this paper, we present an exploratory initial investigation of ways to support user-driven, ad-hoc data integration in PIM tools, towards opening up for use the emerging ecosystem of structured data now available via APIs and structured data feeds on the Web.  We conducted an exploratory, sequential, mixed-method study, starting with two pre-studies focusing on blah and blah, finding that blah ad blah.  These

designed and evaluated DataPalette.  
% We find that the ``light-touch'' data integration mechanisms introduced allow people to effectively work with and combine information from multiple sources, and more thoroughly justify their choices 
%% exploratory, sequential mixed-method study of 
\end{abstract}

@@

We performed an exploratory sequential mixed-method study to help us design our contribution. For our first pre-study, we sought an updated understanding on the use of multiple information sources in information gathering on the Web. There were two driving questions behind this inquiry; first, were people increasingly relying only on a handful of ``supersites'' (Facebook, Wikipedia), or searching across distributed sources of information?  If the former were true, merely integrating PIM tools with the small numbr of supersites would provide greater benefit than tackling the substantially more challenging problem of integrating data from arbitrary sources on the Web.  Second, why did people choose a single or multiple sources for information gathering?  If a number of websites were used, why was this preferred over a single source?

@@

\subsubsection{Results - Heterogeneous Data Tasks}
The participants, recruited informally via word of mouth, consisted of 7 male and 1 female. They were split evenly into two age groups of 18--25 and 26--32.   
% mention # that were computer scientists here?
